Analysis on the Correlations between the efforts made by the Staff of Toronto's Central Intake Line and Toronto's Homeless Death Counts

### 2024-01-24 outputs/paper/paper.qmd
Editted paper title

---
title: "Some Correlations were Found between the efforts made by the Staff of Toronto's Central Intake Line and Toronto's Homeless Death Counts"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/central_intake_calls_and_homeless_death_count.git"
date: today
date-format: long
abstract: "For the City of Toronto, the physical well-being of its local homeless population has always been one of its primary focuses. Numerous social efforts, funded by the City, were made in attempts to reduce the death rate of the local homeless population. In order to visualize the magnitude of social impact enforced by the City of Toronto, analyses were performed to investigate the correlation between the efforts made by the staff of Toronto’s Central Intake Line and the monthly homeless death counts between November 2020 to June 2023 using data from OpenDataToronto. Staff efforts such as the number of calls coded, number of referral to shelter, and number of information for homelessness prevention, were documented and compared against the monthly homeless death counts. An inverse correlation is found between the number of calls coded and the homeless death count. No discernible correlations were found between coded call types of interest and the monthly homeless death counts."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Analysis on the Correlations between the efforts made by the Staff of Toronto's Central Intake Line and Toronto's Homeless Death Counts"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/central_intake_calls_and_homeless_death_count.git"
date: today
date-format: long
abstract: "For the City of Toronto, the physical well-being of its local homeless population has always been one of its primary focuses. Numerous social efforts, funded by the City, were made in attempts to reduce the death rate of the local homeless population. In order to visualize the magnitude of social impact enforced by the City of Toronto, analyses were performed to investigate the correlation between the efforts made by the staff of Toronto’s Central Intake Line and the monthly homeless death counts between November 2020 to June 2023 using data from OpenDataToronto. Staff efforts such as the number of calls coded, number of referral to shelter, and number of information for homelessness prevention, were documented and compared against the monthly homeless death counts. An inverse correlation is found between the number of calls coded and the homeless death count. No discernible correlations were found between coded call types of interest and the monthly homeless death counts."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
